Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
fix
adjusted todo

Essentially, the synthesis problem we are trying to solve is the following:
find a digital controller denoted by  $N_c$ and $D_c$ that
makes the closed-loop system stable 
for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
the uncertainty $(\Delta N_G, \Delta D_G)$ represents $x$.

\red{[clear elucidation of the domain]}

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
Note that, similar to the rest of the paper, we use the notation 
$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

>>>>

Essentially, the synthesis problem we are trying to solve is the following:
find a digital controller denoted by  $N_c$ and $D_c$ that
makes the closed-loop system stable 
for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
Note that, similar to the rest of the paper, we use the notation 
$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
$(\Delta N_G, \Delta D_G)$ represents $x$.

\red{[clear elucidation of the mapping between this and the domains used 
in the general description of the synthesiser]}

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.
